\thetitle

### 2013-06-19 tfpie/tfpie.tex
Tweaks to abstract.

\begin{abstract}
We propose a bridge between functional and object-oriented programming
in the first-year curriculum.  Traditionally, curricula that begin
with functional programming transition to a professional, usually
object-oriented, language in the second course.  This transition poses
 obstacles for students, and often results in confusing the
details of development environments, syntax, and libraries with the
fundamentals of OO programming 
that the course focuses on.  Our proposal instead begins
the second course with a sequence of custom teaching languages which
minimize the transition from the first course, and allow students to
focus on core ideas.  We then transition to Java half-way through
the course, at which point students have a strong command of the basic
principles.  We have 3 years of experience with this course, with
 notable success.
\end{abstract}

>>>>

\begin{abstract}
We propose a bridge between functional and object-oriented programming
in the first-year curriculum.  Traditionally, curricula that begin
with functional programming transition to a professional, usually
object-oriented, language in the second course.  This transition poses
obstacles for students, and often results in confusing the details of
development environments, syntax, and libraries with the fundamentals
of OO programming that the course should focus on.  Instead, we
propose to begin the second course with a sequence of custom teaching
languages which minimize the transition from the first course, and
allow students to focus on core ideas.  After working through the
sequence of pedagogical languages, we then transition to Java, at
which point students have a strong command of the basic principles.
We have 3 years of experience with this course, with notable success.
\end{abstract}
